sta303-hw1

### 2025-02-10 sta303-hw1.Rmd
update

knitr::kable(coef_summary, caption = "Comparison of the log-rate ratios and 95% confidence intervals for Negative Binomial model relating literacy and age at marriage to the number of children, with an offset for years married. The results indicate similar trends as the Poisson model, with literacy being significant, and age at marriage having mixed effects. The reference category for age at marriage is 18 to 20 years.", digits = 3, align = "c") %>%
  kableExtra::kable_styling(full_width = FALSE, position = "center") %>%
  kableExtra::column_spec(1, bold = TRUE)

>>>>

knitr::kable(coef_summary, caption = "Comparison of the log-rate ratios and 95% confidence intervals for a Poisson regression model examining the relationship between literacy, age at marriage, and the number of children, adjusting for the duration of marriage as an offset. The model includes literacy as a categorical predictor and age at marriage categorized into multiple groups, with '18 to 20 years' serving as the reference category. The results indicate a significant positive association between literacy and the number of children, while the effects of age at marriage vary across categories. Specifically, individuals married at ages 22 to 25 show a statistically significant negative association compared to the reference group. Other age categories exhibit varying degrees of association, but not all reach statistical significance at the 0.05 level. The findings suggest that literacy status may play a critical role in shaping fertility outcomes, while the influence of age at marriage is more nuanced. Interpretation of these effects should consider potential confounders and socio-demographic contexts. The standard errors and z-values provide insights into the precision of estimates, and p-values indicate the significance levels of each coefficient..", digits = 3, align = "c") %>%
  kableExtra::kable_styling(full_width = FALSE, position = "center") %>%
  kableExtra::column_spec(1, bold = TRUE)
